\typeout{ ====================================================================}
\typeout{ This is file publications, created at Thu 24 Jan 18:26:56 2013 }
\typeout{ Andre Anjos <andre.dos.anjos@gmail.com> }
\typeout{ ====================================================================}

\section{Quick remarks on publications}

\cvitem{H-Index}{$=$ 10. See \href{http://scholar.google.com/citations?hl=en&user=pAfLhMoAAAAJ}{my Google Scholar page}}

\cvitem{Articles}{$\sim$30\% are journals. I authored and co-authored total of
78, with 25 journals, 48 conference articles, 2 technical reports and 3 thesis
written (graduation, masters, Ph.D.). I'm first author on $\sim$25\% of
the publications listed on the next section.}

\cvitem{Most Cited}{The 2 most cited articles are collaboration articles
from the ATLAS experiment, CERN. They are written by many authors and provide
similar impact.}

\cvitem{Ph.D.}{The third most cited article (29 citations) corresponds to my
Ph.D. thesis journal article.}

\cvitem{Idiap}{The first article written by me while at Idiap has 14 citations
(published on October 2011).}

\cvitem{Recent work}{Since I started in June 2010, I have authored and
co-authored 5 manuscripts while at Idiap.}

\cvitem{On the pipe}{I have 4 other publications waiting review (2 conference
articles and 2 journal articles), not listed on the next section.
\href{https://publications.idiap.ch/index.php}{You can access them} through
Idiap's publication portal, while at Idiap. I'm currently working on 2 book
chapters and another journal article.}

\cvitem{Availability}{All publications have a link that can be used to download
the respective document.}

\typeout{ *************** End of file publications *************** }
